---
title: "SCENA Survey Cleaning"
author: "Terrace Ewinghill"
date: "10/18/2022"
output: html_document
---

# LOAD PACKAGES AND THE DATA
```{r}
# Clear global environment
rm(list=ls())

# Load packages
library(readxl)
library(tidyverse)
library(psych)
library(dplyr)
library(tidyr)
library(readr)
library(stringr)


# getwd()
# Load the data and turn the empty strings into NAs
data <- read.csv('path/to/file/here', na.strings = c("NA", ""))

labels <- read_csv("path/to/file/here")



```


# EXPLORE THE DATA & FIX MINOR TYPOS
```{r}

# What are the variable names?
# names(data)

data <- data %>% rename(
  `YD_8` = `YD_8Â.`,
  `NR_10` = `NR_10Â.`
  )
 
# names(data)

# What types of variables do we have in this data frame?
# str(data)

# This data frame is really large.  Perhaps using str() isn't the best option.

# What are some overall trends in the data?  (Ex: mean, sd, etc.)
# describe(data)



```
# FILTERS AND EXCLUSIONS

```{r}

# Keep the data labels as a reference
data_labels <- data[1:2,]

# class(data_labels)


# Subset the data to exclude the data labels (which were the first two rows)
# This code will need to be adjusted to include all rows for the full data set
data <- data[3:3623,]

# Select the relevant columns
data <- data %>% select(c(UserLanguage, COUNTY:ZIP_2))

# Exclude folks who have been identified as needed to be excluded.
# I confirmed using the filter feature in Excel that this is working as intended
data <- data %>% filter(is.na(EXCLUDE))

```

# CREATE NUMERIC EQUIVALENTS
```{r}
# For the likert scale questions, convert the answers to numeric versions
# Identify which columns should be converted to numerical values
data_numeric <- data %>% mutate_at(c(5:31, 33: 47,49:71,73:94,96:112), ~ case_when(
  . == "A lot" ~ 3,
  . == "Some" ~ 2,
  . == "A little bit" ~ 1,
  . == "Nothing" ~ 0,
  . == "Extremely" ~ 4, 
  . == "Very" ~ 3,
  . == "Somewhat" ~ 2,
  . == "A little" ~ 1, 
  . == "No at all" ~ 0,
  . == "Not at all" ~ 0,
  . == "Don't know" ~ 999))

# Recode the 999s as NA
data_numeric[data_numeric==999] <- NA


```


# Rename UserLanguage
```{r}

data_numeric <- data_numeric %>%
  mutate(UserLanguage = case_when(
    UserLanguage == "EN" ~ "English",
    UserLanguage == "ES" ~ "Spanish",
    TRUE ~ UserLanguage
  ))

  
```


# COOPERATIVE EXTENSION EXPOSURE LABELS
```{r}
data_numeric <- data_numeric %>% 
  mutate(
    CE_EXPOSED = case_when(
      is.na(DEM_1) & is.na(DEM_2) & is.na(DEM_3) & is.na(DEM_4) ~ "No Response",
      DEM_1 == "Some" | DEM_1 == "A lot" | DEM_2 == "Yes" | DEM_3 == "Yes" | DEM_4 == "Yes" ~ "Yes",
      TRUE ~ "No"
    )
  )

data_numeric %>% count(CE_EXPOSED)

data_numeric <- data_numeric %>% 
  mutate(
    CE_USER = case_when(
      is.na(DEM_2) & is.na(DEM_3) & is.na(DEM_4) ~ "No Response",
      DEM_2 == "Yes" | DEM_3 == "Yes" | DEM_4 == "Yes" ~ "Yes",
      TRUE ~ "No"
    )
  )

```

# CREATE VARIABLE FOR FOLKS WHO DID NOT RESPOND TO RACE/ETHNICITY
```{r}
# First, account for everyone who selected at least one race/ethnicity
# Then account for folks who did not respond even in text form

data_numeric <- data_numeric %>% 
  mutate(
    `Prefer not to answer multiple choice` = if_else(
      if_all(c(DEM_10_1, DEM_10_2, DEM_10_3, DEM_10_4, DEM_10_5, DEM_10_6, DEM_10_7), ~ is.na(.)),
      1,
      0
    )
  )

# Options for checking the data
# table(data_numeric$No Response)
# data_NR_mc <- data_numeric %>% select(DEM_10_1: DEM_10_7, `Prefer not to answer multiple choice`) %>% print()

```

# RACE/ETHNICITY BINARY VARIABLES
```{r}

data_numeric <- data_numeric %>%
  mutate(AIAN = case_when(
    DEM_10_1 == "American Indian or Alaska Native" | RACE_ETH == "American Indian or Alaska Native" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))

# Code to check whether this is working as intended
# data_AIAN <- data_numeric %>% select(DEM_10_1, RACE_ETH,`Prefer not to answer multiple choice` , `American Indian or Alaska Native`)

# data_AIAN %>% filter(is.na(RACE_ETH) & `Prefer not to answer multiple choice` == 1) %>% print()

# data_numeric %>% count(DEM_10_2, sort = TRUE)

# data_numeric <- data_numeric %>% mutate(
#   `American Indian or Alaska Native` = ifelse(
#     str_detect(DEM_10_1, pattern = "Native Hawaiian or Other Pacific Islander) | 
#                   str_detect(RACE_ETH, pattern = "Native Hawaiian or Other Pacific Islander"),1,0))

data_numeric <- data_numeric %>%
  mutate(NHPI = case_when(
    DEM_10_2 == "Native Hawaiian or Other Pacific Islander" | RACE_ETH == "Native Hawaiian or Other Pacific Islander" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))


# data_NHPI <- data_numeric %>% select(DEM_10_2, RACE_ETH, `Native Hawaiian or Pacific Islander`)

# data_numeric %>% count(DEM_10_3, sort = TRUE)

# unique(data_numeric$RACE_ETH)


data_numeric <- data_numeric %>%
  mutate(WH = case_when(
    DEM_10_3 == "White" | RACE_ETH == "White" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))

# data_white <- data_numeric %>% select(DEM_10_3, RACE_ETH,`Prefer not to answer multiple choice`, White) %>% print()


# data_numeric %>% count(DEM_10_4, sort = TRUE)

data_numeric <- data_numeric %>%
  mutate(AS = case_when(
    DEM_10_4 == "Asian" | RACE_ETH == "Asian" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))

# data_Asian <- data_numeric %>% select(DEM_10_4, RACE_ETH, Asian, `Prefer not to answer multiple choice`) %>% print()
# data_numeric %>% count(DEM_10_5, sort = TRUE)

data_numeric <- data_numeric %>%
  mutate(BL = case_when(
    DEM_10_5 == "Black or African American" | RACE_ETH == "Black or African American" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))


# data_Black <- data_numeric %>% select(DEM_10_5, RACE_ETH, Black, `Prefer not to answer multiple choice`)

# data_numeric %>% count(DEM_10_6, sort = TRUE)

data_numeric <- data_numeric %>%
  mutate(HL = case_when(
    DEM_10_6 == "Hispanic or Latino" | RACE_ETH == "Hispanic or Latino" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))

# data_Latinx <- data_numeric %>% select(DEM_10_6, RACE_ETH, Latinx)

data_numeric <- data_numeric %>%
  mutate(MR = case_when(RACE_ETH == "Multiracial" ~ 1,
    `Prefer not to answer multiple choice` == 1 & (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ NA_real_,
    TRUE ~ 0
  ))
  
# data_numeric %>% count(DEM_10_7, sort = TRUE)

# unique(data_numeric$RACE_ETH)

# str(data_numeric)
```


# Prefer not to answer the race/ethnicity questions in general
```{r}

data_numeric <- data_numeric %>% 
  mutate(
    NR = case_when(`Prefer not to answer multiple choice` == 1 & 
                                      (RACE_ETH == "NR" | is.na(RACE_ETH)) ~ 1, 
                                   TRUE ~ 0)
  )

# #data_numeric %>% 
#   select(RACE_ETH, `Prefer not to answer multiple choice`, `Prefer not to answer`) %>% 
#   print()


```


# ADD THE 'EXPERT' LABELS
```{r}

# We did not end up using these labels because we didn't think it represented 'experts' afterall
# Keeping it here as a reference nonetheless

# AGRICULTURE
# LIVE – Farm OR Ranch  OR 
# AG_KNW – 2 or more  OR 
# DEM_12_1 = Farming OR 
# DEM_12_2 = Ranching  

data_numeric <- data_numeric %>% mutate(
  AG_EXPERT = ifelse(LIVE == "Farm or ranch" |
                AG_KNW >= 2 |
                DEM_12_1 == "Farming" |
                DEM_12_2 == "Ranching",1,0))

# AG_exp_data <- data_numeric %>% select(LIVE, AG_KNW, DEM_12_1, DEM_12_2, AG_EXPERT)


# EDUCATION
# ED_KNW (a lot or some) OR 
# DEM_12_4 OR
# DEM_12_5 OR
# DEM_12_6 OR
# DEM_12_7 

data_numeric <- data_numeric %>% mutate(
  ED_EXPERT = ifelse(
                YD_KNW >= 2 |
                DEM_12_4 == "Early Education or Child Care" |
                DEM_12_5 == "K-12 Education" |
                DEM_12_6 == "Social or Community Services (Children and Youth)" |
                DEM_12_7 == "Social or Community Services (Adults)",1,0))

# ED_exp_data <- data_numeric %>% select(YD_KNW, DEM_12_4,DEM_12_5, DEM_12_6, DEM_12_7, ED_EXPERT)

# HEALTH
# FCHS_KNW(a lot or some) OR 
# DEM_12_6 OR
# DEM_12_7 OR
# DEM_12_9 

data_numeric <- data_numeric %>% mutate(
  HLTH_EXPERT = ifelse(
                FCHS_KNW >= 2 |
                DEM_12_6 == "Social or Community Services (Children and Youth)" |
                DEM_12_7 == "Social or Community Services (Adults)" |
                DEM_12_9 == "Health",1,0))

# HLTH_exp_dat <- data_numeric %>% select(FCHS_KNW, DEM_12_6, DEM_12_7, DEM_12_9, HLTH_EXPERT)

# NATURAL RESOURCES
# NR_KNOW(a lot or some) OR 
# DEM_12_3 

data_numeric <- data_numeric %>% mutate(
  NR_EXPERT = ifelse(
                NR_KNW >= 2 |
                DEM_12_3 == "Forestry/Land or Resource Management",1,0))

# NR_exp_data <- data_numeric %>% select(NR_KNW, DEM_12_3, NR_EXPERT)

# COMMUNITY AND ECONOMIC DEVELOPMENT
# CED_KNW(a lot or some) OR 
# DEM_12_8 OR
# DEM_12_6 OR
# DEM_12_7

data_numeric <- data_numeric %>% mutate(
  CD_EXPERT = ifelse(
                CED_KNW >= 2 |
                DEM_12_6 == "Social or Community Services (Children and Youth)" |
                DEM_12_7 == "Social or Community Services (Adults)" |
                DEM_12_8 == "Public sector (e.g., government)",1,0))

# CD_exp_data <- data_numeric %>% select(CED_KNW, DEM_12_6, DEM_12_6, DEM_12_7, DEM_12_8, CD_EXPERT)


```

# TOPICAL EXPERIENCE
```{r}


# AGRICULTURE
# LIVE – Farm OR Ranch 
# DEM_12_1 = Farming OR 
# DEM_12_2 = Ranching  
 
data_numeric <- data_numeric %>% 
  mutate(
    AG_EXPERIENCE = ifelse(
      LIVE == "Farm or ranch" |
      DEM_12_1 == "Farming" |
      DEM_12_2 == "Ranching",
      1,
      ifelse(is.na(LIVE) | is.na(DEM_12_1) | is.na(DEM_12_2), NA_integer_, 0)
    )
  )




# EDUCATION
# DEM_12_4 OR
# DEM_12_5 OR
# DEM_12_6 OR
# DEM_12_7 

data_numeric <- data_numeric %>% 
  mutate(
    ED_EXPERIENCE = ifelse(
      is.na(DEM_12_4) & is.na(DEM_12_5) & is.na(DEM_12_6) & is.na(DEM_12_7),
      NA_integer_,
      ifelse(
        DEM_12_4 == "Early Education or Child Care" |
        DEM_12_5 == "K-12 Education" |
        DEM_12_6 == "Social or Community Services (Children and Youth)" |
        DEM_12_7 == "Social or Community Services (Adults)",
        1,
        0
      )
    )
  )

# HEALTH
# DEM_12_6 OR
# DEM_12_7 OR
# DEM_12_9 

data_numeric <- data_numeric %>% 
  mutate(HLTH_EXPERIENCE = case_when(
    DEM_12_6 == "Social or Community Services (Children and Youth)" |
    DEM_12_7 == "Social or Community Services (Adults)" |
    DEM_12_9 == "Health" ~ 1,
    is.na(DEM_12_6) & is.na(DEM_12_7) & is.na(DEM_12_9) ~ NA_real_,
    TRUE ~ 0
  ))

# NATURAL RESOURCES

# DEM_12_3 

data_numeric <- data_numeric %>% 
  mutate(NR_EXPERIENCE = case_when(
    is.na(DEM_12_3) ~ NA_real_,
    DEM_12_3 == "Forestry/Land or Resource Management" ~ 1,
    TRUE ~ 0
  ))


# NR_exp_data <- data_numeric %>% select(NR_KNW, DEM_12_3, NR_EXPERT)

# COMMUNITY AND ECONOMIC DEVELOPMENT
# DEM_12_8 OR
# DEM_12_6 OR
# DEM_12_7

data_numeric <- data_numeric %>% 
  mutate(CD_EXPERIENCE = case_when(
    DEM_12_6 == "Social or Community Services (Children and Youth)" |
    DEM_12_7 == "Social or Community Services (Adults)" |
    DEM_12_8 == "Public sector (e.g., government)" ~ 1,
    all(is.na(c(DEM_12_6, DEM_12_7, DEM_12_8))) ~ NA_real_,
    TRUE ~ 0
  ))

```


# TOPICAL KNOWLEDGE
```{r}

# AGRICULTURE
 # AG_KNW – 2 or more

data_numeric <- data_numeric %>% 
  mutate(
    AG_KNOWLEDGE = if_else(is.na(AG_KNW), NA_real_,
                           if_else(AG_KNW >= 2, 1, as.double(0)))
  )

# AG_knw_data <- data_numeric %>% select(AG_KNW, AG_KNOWLEDGE)


# EDUCATION
# ED_KNW (a lot or some) 


data_numeric <- data_numeric %>% 
  mutate(
    ED_KNOWLEDGE = if_else(is.na(YD_KNW), NA_real_,
                           if_else(YD_KNW >= 2, 1, as.double(0)))
  )

# data_numeric <- data_numeric %>% mutate(
#   ED_KNOWLEDGE = ifelse(
#                 YD_KNW >= 2,1,0))

# ED_knw_data <- data_numeric %>% select(YD_KNW, ED_KNOWLEDGE)

# HEALTH
# FCHS_KNW(a lot or some) 
data_numeric <- data_numeric %>% 
  mutate(
    HLTH_KNOWLEDGE = if_else(is.na(FCHS_KNW), NA_real_,
                           if_else(FCHS_KNW >= 2, 1, as.double(0)))
  )

# data_numeric <- data_numeric %>% mutate(
#   HLTH_KNOWLEDGE = ifelse(
#                 FCHS_KNW >= 2,1,0))

# HLTH_knw_dat <- data_numeric %>% select(FCHS_KNW, HLTH_KNOWLEDGE)

# NATURAL RESOURCES
# NR_KNOW(a lot or some) 

data_numeric <- data_numeric %>% 
  mutate(
    NR_KNOWLEDGE = if_else(is.na(NR_KNW), NA_real_,
                           if_else(NR_KNW >= 2, 1, as.double(0)))
  )

# data_numeric <- data_numeric %>% mutate(
#   NR_KNOWLEDGE = ifelse(
#                 NR_KNW >= 2,1,0))

# NR_knw_data <- data_numeric %>% select(NR_KNW, NR_KNOWLEDGE)

# COMMUNITY AND ECONOMIC DEVELOPMENT
# CED_KNW(a lot or some) 
data_numeric <- data_numeric %>% 
  mutate(
    CD_KNOWLEDGE = if_else(is.na(CED_KNW), NA_real_,
                           if_else(CED_KNW >= 2, 1, as.double(0)))
  )
# 
# data_numeric <- data_numeric %>% mutate(
#   CD_KNOWLEDGE = ifelse(
#                 CED_KNW >= 2,1,0))

# CD_knw_data <- data_numeric %>% select(CED_KNW, CD_KNOWLEDGE)


```

# LIVE COLLAPSED
```{r}

# To protect tribal data, we collapsed 'tribal' into rural for the public data dashboard

# unique(data_numeric$LIVE)


data_numeric <- data_numeric %>% mutate(
  LIVE_V2 = case_when(
    LIVE == "City" | LIVE == "Suburb of a city" ~ "Urban",
    LIVE == "Rural (not a farm or ranch)" | LIVE == "Farm or ranch" | LIVE == "Small town" ~ "Rural",
    LIVE == "Tribal lands" ~ "Tribal",
    is.na(LIVE) ~ NA_character_,
    TRUE ~ NA_character_
  )
)



data_numeric <- data_numeric %>% mutate(
  LIVE_V3 = case_when(
    LIVE == "City" | LIVE == "Suburb of a city" ~ "Urban",
    LIVE == "Rural (not a farm or ranch)" | LIVE == "Farm or ranch" | LIVE == "Small town" | LIVE == "Tribal lands" ~ "Rural",
    is.na(LIVE) ~ NA_character_,
    TRUE ~ NA_character_
  )
)

  
# LIVE_v2_data <- data_numeric %>% select(LIVE, LIVE_V2)


```


# BINARY VARIABLE FOR EXTREMELY AND VERY IMPORTANT FOR ALL TOPICS (not the KNW_ ones)
# FCHS
```{r}

# FCHS extremely, very important 
data_numeric <- data_numeric %>% mutate(
  FCHS_1_Eimp = ifelse(
                FCHS_1 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_1_EVimp = ifelse(
                FCHS_1 >= 3,1,0))

# FCHS_1_data <- data_numeric %>% select(FCHS_1, FCHS_1_Eimp, FCHS_1_EVimp)
data_numeric <- data_numeric %>% mutate(
  FCHS_2_Eimp = ifelse(
                FCHS_2 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_2_EVimp = ifelse(
                FCHS_2 >= 3,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_3_Eimp = ifelse(
                FCHS_3 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_3_EVimp = ifelse(
                FCHS_3 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_4_Eimp = ifelse(
                FCHS_4 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_4_EVimp = ifelse(
                FCHS_4 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_5_Eimp = ifelse(
                FCHS_5 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_5_EVimp = ifelse(
                FCHS_5 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_6_Eimp = ifelse(
                FCHS_6 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_6_EVimp = ifelse(
                FCHS_6 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_7_Eimp = ifelse(
                FCHS_7 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_7_EVimp = ifelse(
                FCHS_7 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_8_Eimp = ifelse(
                FCHS_8 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_8_EVimp = ifelse(
                FCHS_8 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_9_Eimp = ifelse(
                FCHS_9 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_9_EVimp = ifelse(
                FCHS_9 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_10_Eimp = ifelse(
                FCHS_10 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_10_EVimp = ifelse(
                FCHS_10 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_11_Eimp = ifelse(
                FCHS_11 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_11_EVimp = ifelse(
                FCHS_11 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_12_Eimp = ifelse(
                FCHS_12 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_12_EVimp = ifelse(
                FCHS_12 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_13_Eimp = ifelse(
                FCHS_13 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_13_EVimp = ifelse(
                FCHS_13 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_14_Eimp = ifelse(
                FCHS_14 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_14_EVimp = ifelse(
                FCHS_14 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_15_Eimp = ifelse(
                FCHS_15 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_15_EVimp = ifelse(
                FCHS_15 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_16_Eimp = ifelse(
                FCHS_16 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_16_EVimp = ifelse(
                FCHS_16 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_17_Eimp = ifelse(
                FCHS_17 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_17_EVimp = ifelse(
                FCHS_17 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_18_Eimp = ifelse(
                FCHS_18 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_18_EVimp = ifelse(
                FCHS_18 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_19_Eimp = ifelse(
                FCHS_19 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_19_EVimp = ifelse(
                FCHS_19 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_20_Eimp = ifelse(
                FCHS_20 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_20_EVimp = ifelse(
                FCHS_20 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_21_Eimp = ifelse(
                FCHS_21 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_21_EVimp = ifelse(
                FCHS_21 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_22_Eimp = ifelse(
                FCHS_22 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_22_EVimp = ifelse(
                FCHS_22 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_23_Eimp = ifelse(
                FCHS_23 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_23_EVimp = ifelse(
                FCHS_23 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_24_Eimp = ifelse(
                FCHS_24 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_24_EVimp = ifelse(
                FCHS_24 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_25_Eimp = ifelse(
                FCHS_25 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_25_EVimp = ifelse(
                FCHS_25 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  FCHS_26_Eimp = ifelse(
                FCHS_26 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  FCHS_26_EVimp = ifelse(
                FCHS_26 >= 3,1,0))



```


# BINARY VARIABLE FOR EXTREMELY AND VERY IMPORTANT FOR ALL TOPICS (not the KNW_ ones)
# EDUCATION/YOUTH DEVELOPMENT
```{r}
data_numeric <- data_numeric %>% mutate(
  YD_1_Eimp = ifelse(
                YD_1 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_1_EVimp = ifelse(
                YD_1 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_2_Eimp = ifelse(
                YD_2 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_2_EVimp = ifelse(
                YD_2 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_3_Eimp = ifelse(
                YD_3 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_3_EVimp = ifelse(
                YD_3 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_4_Eimp = ifelse(
                YD_4 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_4_EVimp = ifelse(
                YD_4 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_5_Eimp = ifelse(
                YD_5 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_5_EVimp = ifelse(
                YD_5 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_6_Eimp = ifelse(
                YD_6 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_6_EVimp = ifelse(
                YD_6 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_7_Eimp = ifelse(
                YD_7 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_7_EVimp = ifelse(
                YD_7 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_8_Eimp = ifelse(
                YD_8 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_8_EVimp = ifelse(
                YD_8 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_9_Eimp = ifelse(
                YD_9 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_9_EVimp = ifelse(
                YD_9 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_10_Eimp = ifelse(
                YD_10 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_10_EVimp = ifelse(
                YD_10 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_11_Eimp = ifelse(
                YD_11 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_11_EVimp = ifelse(
                YD_11 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_12_Eimp = ifelse(
                YD_12 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_12_EVimp = ifelse(
                YD_12 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_13_Eimp = ifelse(
                YD_13 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_13_EVimp = ifelse(
                YD_13 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  YD_14_Eimp = ifelse(
                YD_14 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  YD_14_EVimp = ifelse(
                YD_14 >= 3,1,0))
```

# BINARY VARIABLE FOR EXTREMELY AND VERY IMPORTANT FOR ALL TOPICS (not the KNW_ ones)
# AGRICULTURE
```{r}
data_numeric <- data_numeric %>% mutate(
  AG_1_Eimp = ifelse(AG_1 == 4, 1,0))

data_numeric <- data_numeric %>% mutate(
  AG_1_EVimp = ifelse(
                AG_1 >= 3,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_2_Eimp = ifelse(
                AG_2 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_2_EVimp = ifelse(
                AG_2 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_3_Eimp = ifelse(
                AG_3 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_3_EVimp = ifelse(
                AG_3 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_4_Eimp = ifelse(
                AG_4 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_4_EVimp = ifelse(
                AG_4 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_5_Eimp = ifelse(
                AG_5 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_5_EVimp = ifelse(
                AG_5 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_6_Eimp = ifelse(
                AG_6 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_6_EVimp = ifelse(
                AG_6 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_7_Eimp = ifelse(
                AG_7 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_7_EVimp = ifelse(
                AG_7 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_8_Eimp = ifelse(
                AG_8 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_8_EVimp = ifelse(
                AG_8 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_9_Eimp = ifelse(
                AG_9 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_9_EVimp = ifelse(
                AG_9 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_10_Eimp = ifelse(
                AG_10 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_10_EVimp = ifelse(
                AG_10 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_11_Eimp = ifelse(
                AG_11 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_11_EVimp = ifelse(
                AG_11 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_12_Eimp = ifelse(
                AG_12 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_12_EVimp = ifelse(
                AG_12 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_13_Eimp = ifelse(
                AG_13 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_13_EVimp = ifelse(
                AG_13 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_14_Eimp = ifelse(
                AG_14 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_14_EVimp = ifelse(
                AG_14 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_15_Eimp = ifelse(
                AG_15 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_15_EVimp = ifelse(
                AG_15 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_16_Eimp = ifelse(
                AG_16 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_16_EVimp = ifelse(
                AG_16 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_17_Eimp = ifelse(
                AG_17 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_17_EVimp = ifelse(
                AG_17 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_18_Eimp = ifelse(
                AG_18 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_18_EVimp = ifelse(
                AG_18 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_19_Eimp = ifelse(
                AG_19 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_19_EVimp = ifelse(
                AG_19 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_20_Eimp = ifelse(
                AG_20 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_20_EVimp = ifelse(
                AG_20 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  AG_22_Eimp = ifelse(
                AG_22 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  AG_22_EVimp = ifelse(
                AG_22 >= 3,1,0))


```
# BINARY VARIABLE FOR EXTREMELY AND VERY IMPORTANT FOR ALL TOPICS (not the KNW_ ones)
# NATURAL RESOURCES
```{r}
data_numeric <- data_numeric %>% mutate(
  NR_1_Eimp = ifelse(
                NR_1 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_1_EVimp = ifelse(
                NR_1 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_2_Eimp = ifelse(
                NR_2 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_2_EVimp = ifelse(
                NR_2 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_3_Eimp = ifelse(
                NR_3 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_3_EVimp = ifelse(
                NR_3 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_4_Eimp = ifelse(
                NR_4 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_4_EVimp = ifelse(
                NR_4 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_5_Eimp = ifelse(
                NR_5 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_5_EVimp = ifelse(
                NR_5 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_6_Eimp = ifelse(
                NR_6 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_6_EVimp = ifelse(
                NR_6 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_7_Eimp = ifelse(
                NR_7 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_7_EVimp = ifelse(
                NR_7 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_8_Eimp = ifelse(
                NR_8 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_8_EVimp = ifelse(
                NR_8 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_9_Eimp = ifelse(
                NR_9 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_9_EVimp = ifelse(
                NR_9 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_10_Eimp = ifelse(
                NR_10 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_10_EVimp = ifelse(
                NR_10 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_11_Eimp = ifelse(
                NR_11 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_11_EVimp = ifelse(
                NR_11 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_12_Eimp = ifelse(
                NR_12 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_12_EVimp = ifelse(
                NR_12 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_13_Eimp = ifelse(
                NR_13 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_13_EVimp = ifelse(
                NR_13 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_14_Eimp = ifelse(
                NR_14 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_14_EVimp = ifelse(
                NR_14 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_15_Eimp = ifelse(
                NR_15 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_15_EVimp = ifelse(
                NR_15 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_16_Eimp = ifelse(
                NR_16 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_16_EVimp = ifelse(
                NR_16 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_17_Eimp = ifelse(
                NR_17 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_17_EVimp = ifelse(
                NR_17 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_18_Eimp = ifelse(
                NR_18 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_18_EVimp = ifelse(
                NR_18 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_19_Eimp = ifelse(
                NR_19 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_19_EVimp = ifelse(
                NR_19 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_20_Eimp = ifelse(
                NR_20 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_20_EVimp = ifelse(
                NR_20 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  NR_21_Eimp = ifelse(
                NR_21 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  NR_21_EVimp = ifelse(
                NR_21 >= 3,1,0))

```

# BINARY VARIABLE FOR EXTREMELY AND VERY IMPORTANT FOR ALL TOPICS (not the KNW_ ones)
# COMMUNITY AND ECONOMIC DEVELOPMENT
```{r}
data_numeric <- data_numeric %>% mutate(
  CED_1_Eimp = ifelse(
                CED_1 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_1_EVimp = ifelse(
                CED_1 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_2_Eimp = ifelse(
                CED_2 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_2_EVimp = ifelse(
                CED_2 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_3_Eimp = ifelse(
                CED_3 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_3_EVimp = ifelse(
                CED_3 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_4_Eimp = ifelse(
                CED_4 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_4_EVimp = ifelse(
                CED_4 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_5_Eimp = ifelse(
                CED_5 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_5_EVimp = ifelse(
                CED_5 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_6_Eimp = ifelse(
                CED_6 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_6_EVimp = ifelse(
                CED_6 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_7_Eimp = ifelse(
                CED_7 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_7_EVimp = ifelse(
                CED_7 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_8_Eimp = ifelse(
                CED_8 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_8_EVimp = ifelse(
                CED_8 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_9_Eimp = ifelse(
                CED_9 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_9_EVimp = ifelse(
                CED_9 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_10_Eimp = ifelse(
                CED_10 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_10_EVimp = ifelse(
                CED_10 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_11_Eimp = ifelse(
                CED_11 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_11_EVimp = ifelse(
                CED_11 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_12_Eimp = ifelse(
                CED_12 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_12_EVimp = ifelse(
                CED_12 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_13_Eimp = ifelse(
                CED_13 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_13_EVimp = ifelse(
                CED_13 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_14_Eimp = ifelse(
                CED_14 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_14_EVimp = ifelse(
                CED_14 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_15_Eimp = ifelse(
                CED_15 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_15_EVimp = ifelse(
                CED_15 >= 3,1,0))
data_numeric <- data_numeric %>% mutate(
  CED_16_Eimp = ifelse(
                CED_16 == 4,1,0))

data_numeric <- data_numeric %>% mutate(
  CED_16_EVimp = ifelse(
                CED_16 >= 3,1,0))

```

# Add NAs to "Prefer not to answer" and "I prefer not to answer" together
```{r}
data_numeric <- data_numeric %>% mutate(
  DEM_13 = case_when(
    is.na(DEM_13) ~ "Prefer not to answer",
    DEM_13 == "I prefer not to answer" ~ "Prefer not to answer",
    TRUE ~ DEM_13
  )
)

```




# Calculate 100% FPL using the variable DEM_13 (Household income) and DEM_5 (number of people living in household)
```{r}

data_numeric <- data_numeric %>% 
  mutate(Low_Income_FPL_100 = case_when(
    is.na(DEM_5) | is.na(DEM_13) ~ NA_real_,
    DEM_5 == 1 & DEM_13 <= 14580 ~ 1,
    DEM_5 == 2 & DEM_13 <= 19720 ~ 1,
    DEM_5 == 3 & DEM_13 <= 24860 ~ 1,
    DEM_5 == 4 & DEM_13 <= 30000 ~ 1,
    DEM_5 == 5 & DEM_13 <= 35140 ~ 1,
    DEM_5 == 6 & DEM_13 <= 40280 ~ 1,
    DEM_5 == 7 & DEM_13 <= 45420 ~ 1,
    DEM_5 == 8 & DEM_13 <= 50560 ~ 1,
    DEM_5 == 9 & DEM_13 <= 55700 ~ 1,
    DEM_5 == 10 & DEM_13 <= 60840 ~ 1,
    DEM_5 == 11 & DEM_13 <= 65980 ~ 1,
    DEM_5 == 12 & DEM_13 <= 71120 ~ 1,
    DEM_5 == 13 & DEM_13 <= 76260 ~ 1,
    DEM_5 == 14 & DEM_13 <= 81400 ~ 1,
    TRUE ~ 0 
  ))

data_numeric$Low_Income_FPL_100 <- ifelse(data_numeric$Low_Income_FPL_100 == 0, "No", "Yes")




```



# Calculate 185% FPL using the variable DEM_13 (Household income) and DEM_5 (number of people living in household)
```{r}

data_numeric <- data_numeric %>% 
  mutate(Low_Income_FPL_185 = case_when(
    is.na(DEM_5) | is.na(DEM_13) ~ NA_real_, # Set NAs as missing values
    DEM_5 == 1 & DEM_13 <= 26973 ~ 1,
    DEM_5 == 2 & DEM_13 <= 36482 ~ 1,
    DEM_5 == 3 & DEM_13 <= 45991 ~ 1,
    DEM_5 == 4 & DEM_13 <= 55500 ~ 1,
    DEM_5 == 5 & DEM_13 <= 65009 ~ 1,
    DEM_5 == 6 & DEM_13 <= 74518 ~ 1,
    DEM_5 == 7 & DEM_13 <= 84027 ~ 1,
    DEM_5 == 8 & DEM_13 <= 93536 ~ 1,
    DEM_5 == 9 & DEM_13 <= 103045 ~ 1,
    DEM_5 == 10 & DEM_13 <= 112554 ~ 1,
    DEM_5 == 11 & DEM_13 <= 122063 ~ 1,
    DEM_5 == 12 & DEM_13 <= 131572 ~ 1,
    DEM_5 == 13 & DEM_13 <= 141081 ~ 1,
    DEM_5 == 14 & DEM_13 <= 150590 ~ 1,
    TRUE ~ 0 
  ))

data_numeric$Low_Income_FPL_185 <- ifelse(data_numeric$Low_Income_FPL_185 == 0, "No", "Yes")


```

# Create a new bucket variable for AGE
```{r}

data_numeric <- data_numeric %>% 
  mutate(AGE = case_when(
    DEM_9 >= 14 & DEM_9 <= 24 ~ "14-24 years old",
    DEM_9 >= 25 & DEM_9 <= 39 ~ "25-39 years old",
    DEM_9 >= 40 & DEM_9 <= 54 ~ "40-54 years old",
    DEM_9 >= 55 & DEM_9 <= 64 ~ "55-64 years old",
    DEM_9 >= 65 ~ "65 years and older",
    is.na(DEM_9) ~ "Prefer not to answer",
    TRUE ~ "Prefer not to answer"
  ))


```

# Add NA to "Prefer not to answer"
```{r}

data_numeric <- data_numeric %>% mutate(
  DEM_11 = ifelse(is.na(DEM_11), "Prefer not to answer", DEM_11))

```


# Create a new educational attainment variable

```{r}

data_numeric <- data_numeric %>% mutate(
  Bach_or_higher = case_when(
    DEM_11 %in% c("Bachelor's degree", "Graduate or professional degree") ~ "Yes",
    is.na(DEM_11) ~ "No Response",
    TRUE ~ "No"
  )
)

```

# Fix Gender for data viz to show NAs as "no response"
```{r}

data_numeric <- data_numeric %>% mutate(
  Gender = case_when(
    GENDER == "Non-binary Woman" ~ "Non-binary",
    GENDER == "Man" ~ "Man",
    GENDER == "Woman" ~ "Woman",
    GENDER == "Non-binary" ~ "Non-binary",
    is.na(GENDER) ~ "No Response",
    TRUE ~ NA_character_
  )
)

```

# Add a non-response to the information question
```{r}

data_numeric <- data_numeric %>% 
  rowwise() %>%
  mutate(DEM_14_NR = case_when(
             all(is.na(c_across(starts_with("DEM_14")))) ~ "Prefer not to answer",
             any(!is.na(c_across(starts_with("DEM_14")))) ~ NA_character_,
             TRUE ~ NA_character_
  ))


data_DEM_14 <- data_numeric %>% select(DEM_14_1: DEM_14_NR)


# If any of these is not NA, then mark the new value as NA.
# If all of the DEM_14 columns are NA, then write "Prefer not to answer"

```



# data_numeric$Gender %>% count()

# Only select the columns needed for the dashboard
```{r}
data_numeric <- data_numeric %>% 
select(
    COUNTY,
    LIVE_V3,
    UserLanguage,
    DEM_11,
    DEM_13,
    DEM_14_1: DEM_14_10,
    DEM_14_NR,
    Low_Income_FPL_185,
    Gender,
    AGE,
    Bach_or_higher,
    ends_with("EVimp"),
    AIAN,
    AS,
    BL,
    HL,
    MR,
    NHPI,
    WH,
    NR,
    ends_with("EXPERIENCE"),
    ends_with("KNOWLEDGE"), 
    CE_USER,
    CE_EXPOSED,
    all_of(labels$Metric)
  )



```


# Write this data as a CSV
```{r}
# getwd()
write_csv(data_numeric, "path/to/file/file_name_date.csv")

```

# Pin it to the board on R Studio Connect
```{r}
# For our team, we pinned the data on R Studio Connect which is password protected with two-step verification. Even so, this file did not contain identifiable or zipcode level data.

library(pins)
board <- board_connect()
pin_write(board, data_numeric, "file-name", type = "arrow")

```

